Social Network Analysis: Week 3: Degree and Centrality

### 2022-02-19 docs/3. SNA - Assignments/Week3-Distill-Blog_Degree-and-Centrality.Rmd
2.22.22 late on this past weekend's committs

I'm curious to find how Drink Names are linked to
each other by sharing ingredients.

##

1.  <div>

    > -   identify initial network format;
    >
    > -   describe and identify the nodes
    >     including:
    >
    >     -   how many nodes are in the dataset;
    >
    > -   what constitutes a tie or edge
    >     including:
    >
    >     -   how many ties,
    >
    >     -   whether ties are
    >         directed/undirected,
    >
    >     -   whether ties are weighted/binary,
    >
    >     -   and how to interpret the value of
    >         the tie if any.
    >
    >     -   Whether or not there are edge
    >         attributes that might be used to:
    >
    >         -   subset data, or
    >         -   stack multiple networks.

## Working from the example R syntax:

@@

    | Col1 | Col2 | Col3 |
    |------|------|------|
    |      |      |      |
    |      |      |      |
    |      |      |      |

    : Network Maeasure

## *Write up your results briefly:*

##

@@

1.  the relevant statistics and interpretation.
    For example, explaining which node(s) are most
    central and which are least central.
2.  Discuss (with any related evidence) whether or
    not the node(s) behavior is in line with or
    violates expectations based on the degree
    centrality measure.
3.  What do you make of network density and
    centralization measures?\
4.  What about differences in the binary 100
    million threshold network vs valued trade
    flows network.
5.  Check tutorial for other ideas of results to
    discuss.

>>>>

![](https://tenor.com/brZQ5.gif){width="2474"
height="255"}

There is not an organization with the self-imposed
responsibility and authority to standardize the
recopies and classification of cocktails while
maintain records attributing a drinks development
to a specific bar or bartender. Can we use SNA
methods to suss out anecdotal aspects of
contemporary cocktail culture?

To start: I'm curious to see what sort of
relationships exists between Tiki Cocktail
Ingredients? Cocktails are build with specific
ingredients, methods, and presentations to fit
contemporary cocktail culture aesthetics.

*For example:* "gin goes with lime (not lemon);"
but why is that? *Short answer:* European
imperialism and systematic wealth extraction of
the global south. It's the same reason why my
Jamaican Grandmother said "kidney beans go in rice
& peas (not English peas)"

*Another example:* The fictional James Bond being
cited as an authoritative voice on whether a
proper Martini's should be shaken or stirred.
*Short answer:* Cocktails with eggs and milk are
shaken to create foam. Spirit forward drinks tend
to be stirred to limit dilution. *You can shake a
drink with carbonated ingredients if you want to.*

# What makes a Tiki Drink a "Tiki Drink?"

This isn't the "ask 10 people and get 10 different
answers" sort of question, but all of the answers
are based on each person's professionally
(un)informed opinion. As a former bartender - I
believe in the authority of the published opinions
of professional bartenders and [cocktail
historians](https://www.theatlantic.com/health/archive/2010/06/how-to-be-a-drink-historian/58724/).
Their opinion is based in direct experience and
observation of the subject in question. Which is
the sort of thing empiricists do, but since they
are building cocktails instead of a dataset, their
answers are given the same consideration of
qualitative research.

## To start:

## I'm curious to see what sort of relationships exists between Tiki Cocktail Ingredients?

## Cocktails are build with specific ingredients, methods, and presentations to fit contemporary cocktail culture aesthetics.

### *Write up your results briefly:*

### Working from the example R syntax:

@@

<div>

> -   identify initial network format;
>
>     -   **Smuggler's Cove Index was converted
>         into an edgelist**
>
> -   describe and identify the nodes including:
>
>     -   **Smuggler's Cove Edgelist**
>
>         -   **Nodes: 274**
>
>         -   **Edges: 672**
>
> -   what constitutes a tie or edge including:
>
>     -   Ties
>
>         -   Number:
>
>         -   Directed
>
>         -   Binary
>
>     -   interpret the value of the tie if any.
>
>     -    edge attributes that might be used to:
>
>         -   subset data, or
>         -   stack multiple networks.

@@

1.  the relevant statistics and interpretation.

    -   For example, explaining which **node(s)
        are most central and which are least
        central.**

2.  Discuss (with any related evidence) whether or
    not the **node(s) behavior is in line with or
    violates expectations based on the degree
    centrality measure.**

    1.  **What do you make of network density and
        centralization measures?\
        **

        +-----------+--------------+--------+-----------+
        | Analysis  | statnet      | igraph | Plot      |
        +===========+==============+========+===========+
        | Dyad      | Mutual: 1    | 0.0179 | yes       |
        | Census    |              |        |           |
        |           | A            |        |           |
        |           | symmetrical: |        |           |
        |           | 670          |        |           |
        |           |              |        |           |
        |           | Null: 36730  |        |           |
        +-----------+--------------+--------+-----------+
        | Triad     | 0: 3216391   |        |           |
        | Census:   |              |        |           |
        |           | 1: 7879 0    |        |           |
        | All       |              |        |           |
        | Triads in | 2 : 166754   |        |           |
        | Network   |              |        |           |
        |           | 3:           |        |           |
        +-----------+--------------+--------+-----------+
        | Triad     | 3391024      | (undi  | yes       |
        | Census:   |              | rected |           |
        |           |              | graph) |           |
        | total     |              |        |           |
        | number of |              | [1]    |           |
        | all four  |              | 3      |           |
        | triad     |              | 216659 |           |
        | types     |              |        |           |
        |           |              | [2]    |           |
        |           |              | 166486 |           |
        |           |              |        |           |
        |           |              | [11]   |           |
        |           |              | 7879   |           |
        +-----------+--------------+--------+-----------+
        | Tra       | undirected   | Undi   |           |
        | nsitivity |              | rected |           |
        +-----------+--------------+--------+-----------+
        | Local     |              |        |           |
        | tran      |              |        |           |
        | sitivity: |              |        |           |
        | Node List |              |        |           |
        | & Ego     |              |        |           |
        | Network   |              |        |           |
        +-----------+--------------+--------+-----------+
        | Isolates  | no           |        |           |
        +-----------+--------------+--------+-----------+
        | Un        |              | n      |           |
        | directed: |              | umber: |           |
        | Component |              | 1      |           |
        | Structure |              |        |           |
        |           |              | size:  |           |
        |           |              | 274    |           |
        +-----------+--------------+--------+-----------+
        | Directed: |              | 0.01   | yes       |
        | GRAPH:    |              | 671642 |           |
        | Dyad      |              |        |           |
        | Census    |              |        |           |
        +-----------+--------------+--------+-----------+
        |           |              |        | yes       |
        | Directed: |              |        |           |
        | Degree    |              |        |           |
        | C         |              |        |           |
        | entrality |              |        |           |
        +-----------+--------------+--------+-----------+
        | Directed: |              |        | yes       |
        | Be        |              |        |           |
        | tweenness |              |        |           |
        | C         |              |        |           |
        | entrality |              |        |           |
        +-----------+--------------+--------+-----------+
        | Directed: |              |        | yes       |
        | Ei        |              |        |           |
        | genvector |              |        |           |
        | C         |              |        |           |
        | entrality |              |        |           |
        +-----------+--------------+--------+-----------+
        | Directed: |              |        |           |
        | Bonacich  |              |        |           |
        | Ce        |              |        |           |
        | ntrality} |              |        |           |
        +-----------+--------------+--------+-----------+
        |           |              |        |           |
        | Directed: |              |        |           |
        | Page Rank |              |        |           |
        +-----------+--------------+--------+-----------+
        |           |              |        |           |
        +-----------+--------------+--------+-----------+
        |           |              |        |           |
        +-----------+--------------+--------+-----------+

### 2022-02-19 docs/3. SNA - Assignments/Week3_Degree-and-Centrality.Rmd
2.22.22 late on this past weekend's committs

## Write up your results briefly:
*   focus on interpretation of the results. 
*   Don’t list statistics or provide code, 
*  **the goal is to choose a few interesting results and provide an interpretation.**

## Briefly describe the dataset:
1.   identify initial network format; 
2.   describe and identify the nodes 
     including: 
        *  how many nodes are in the dataset; 
3.   what constitutes a tie or edge
     including:
        *  how many ties, 
        *   whether ties are directed/undirected,
        *   whether ties are weighted/binary, 
        *   and how to interpret the value of the tie if any.
        *   Whether or not there are edge attributes 
            that might be used to:
            *   subset data, or 
            *   stack multiple networks. 
Not every feature of the network needs to be described, but **description should orient reader to the network data and provide any necessary context for the results provided.**

## Provide at least two or three noteworthy results, including:
1.   the relevant statistics and interpretation. 
        For example, explaining which node(s) are most central and which are least central. 
2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
3.   What do you make of network density and centralization measures?  
4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
 5.  Check tutorial for other ideas of results to discuss.

>>>>

##        *Write up your results briefly: *
*   focus on interpretation of the results. 
*   Don’t list statistics or provide code, 
*  **the goal is to choose a few interesting results and provide an interpretation.**

##        *Briefly describe the dataset:*
1.   identify initial network format; 
2.   describe and identify the nodes 
     including: 
        *  how many nodes are in the dataset; 
3.   what constitutes a tie or edge
     including:
        *  how many ties, 
        *   whether ties are directed/undirected,
        *   whether ties are weighted/binary, 
        *   and how to interpret the value of the tie if any.
        *   Whether or not there are edge attributes 
            that might be used to:
            *   subset data, or 
            *   stack multiple networks.

##        *Provide at least two or three noteworthy results*, including:
1.   the relevant statistics and interpretation. 
        For example, explaining which node(s) are most central and which are least central. 
2.   Discuss (with any related evidence) whether or not the node(s) behavior is in line with or violates expectations based on the degree centrality measure. 
3.   What do you make of network density and centralization measures?  
4.   What about differences in the binary 100 million threshold network vs valued trade flows network. 
 5.  Check tutorial for other ideas of results to discuss.
